Preprocessing

### 2023-07-14 docs/presentation/preprocess.Rmd
viz: skip saving rds

```{r word clouds}
cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
saveRDS(clouds, file = "data/clouds.rds")
```

@@

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

@@

Q5 (maybe put with Q6's word cloud)

>>>>

```{r word clouds}
cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
clouds <- map(cloud_cols, column_to_cloud) %>%
  set_names(cloud_cols)
# saveRDS(clouds, file = "data/clouds.rds")
```

@@

clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
clouds_q6$Everyone <- clouds$Q6
# saveRDS(clouds_q6, file = "data/clouds_q6.rds")
```

Q5

```{r q5}

```

@@
